---
title: "DGT children first fix"
output:
  html_document:
    df_print: paged
---

# Data preparation

## Load the libraries

```{r include=FALSE}
library(tidyverse)
library(lmerTest)
library(car)
library(emmeans)
```

## Load adults and children data

```{r include=FALSE}
child_df <- read_csv('Children_data.csv')
adult_df <- read_csv('adult_data.csv')
```


Print the number of subjects in each group.

```{r}
child_df %>%
  group_by(age_group, gender) %>%
  summarise(n_distinct(sub))
```

Print their mean age.
```{r}
child_df %>%
  group_by(age_group) %>%
  summarise(avg_age = mean(Age), sd_age = sd(Age))
```


## Preprocess the data

```{r include=FALSE}
children_fix <- child_df %>%
  select(sub, gender, image_no, first_fix, age_group)
```
```{r include=FALSE}
adult_fix <- adult_df %>%
  select(sub, gender, image_no, first_fix) %>%
  mutate(age_group = 'Adults')
```

## Combine the data

Flip the code of dominance, now 1 means choosing the low dominance

```{r include=FALSE}
combined_df <- bind_rows(adult_fix, children_fix)
# flip the code of dominance, now 1 means choosing the low dominance
combined_df$first_fix <- ifelse(combined_df$first_fix == 0, 1, 0)
combined_df <- combined_df %>%
  mutate(across(everything(), factor))
```

# Plot the data

## Compute the percentage

```{r include=FALSE}
sub_data <- combined_df %>%
  group_by(sub, age_group, gender) %>%
  summarise(Percentage = mean(first_fix==1), .groups = 'drop')
```
## The box plot

```{r}
# 1) Open a PDF device (vector) with 600 dpi fallback
cairo_pdf(
  filename            = "Figure5.pdf",  # change as needed
  width               = 6,    # inches
  height              = 4,    # inches
  fallback_resolution = 600   # dpi for any bitmaps
)

# 2) Your plot
ggplot(sub_data, aes(x = age_group, y = Percentage, fill = gender)) +
  geom_boxplot() +
  stat_summary(fun=mean, geom="point", color="green", size=3, shape=18, position=position_dodge(width=0.75)) +
  ylim(0, 1) +
  scale_fill_discrete(labels = c("Female", "Male")) +
  labs(
    x    = "Age Group",
    y    = "Percentage of First Touch on Low Dominance",
    fill = "Gender"
  ) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black")

# 3) Close the device and write the file
dev.off()

```

# Linear Mixed Models

## Model comparisons

Gender and age are normally fixed effects, so we use subject as the random intercept. We didn't include image id in the model because those images are computer-generated and are very similar.

```{r}
# Model with random intercepts for subjects
model1 <- glmer(first_fix ~ gender + age_group + (1 | sub), family = binomial(link = "logit"), data = combined_df)

# Model with random intercepts and possible interactions
model2 <- glmer(first_fix ~ gender * age_group + (1 | sub), family = binomial(link = "logit"), data = combined_df)

```

The model adding the interaction is better.

```{r echo=FALSE}
anova(model1, model2)
```

Then we looked at the results.

```{r echo=FALSE}
summary(model2)
```

Print an anova-style table.

```{r echo=FALSE}
Anova(model2, type='III')
```

## Post hoc

```{r echo=FALSE}
# Get EMMs for gender within each level of age
emm_gender <- emmeans(model2, ~ gender | age_group)

# Pairwise comparisons within each age group
pairs_gender <- pairs(emm_gender, adjust = "tukey")
summary(pairs_gender)
```

```{r echo=FALSE}
# Get EMMs for age within each level of gender
emm_age <- emmeans(model2, ~ age_group | gender)

# Pairwise comparisons within each gender
pairs_age <- pairs(emm_age, adjust = "tukey")
summary(pairs_age)
```

