---
title: "DGT_Time_LMM"
output:
  html_document:
    df_print: paged
---

# Preparations

## Load the libraries

```{r include=FALSE}
library(tidyverse)
library(lmerTest)
library(car)
library(emmeans)
emmeans::emm_options(pbkrtest.limit = 12864, lmerTest.limit = 12864)
```

## Call the function

```{r include=FALSE}
source("compare_lmm_models.R")
```

# Adults

```{r include=FALSE}
adult_df <- read_csv('adult_data.csv')
```

## Face

### Preprocess

```{r include=FALSE}
adult_face <- adult_df %>%
  select(sub, image_no, gender, Time_face_h, Time_face_l) %>%
  pivot_longer(
    cols = c(Time_face_h, Time_face_l),
    names_to = "dominance", 
    values_to = "proportion_time"
  ) %>%
  mutate(dominance = case_when(
    dominance == "Time_face_h" ~ "High",
    dominance == "Time_face_l" ~ "Low"
  ))
```

### Model comparisons

```{r echo=FALSE}
best_model_adult_face <- compare_lmm_models(
  data = adult_face,
  dv = "proportion_time",
  fixed_effects = c("gender", "dominance"),
  random_vars = c("dominance"),
  group_var = "sub"
)
```

### The best model

```{r echo=FALSE}
summary(best_model_adult_face)
Anova(best_model_adult_face, type = 'III')
```


### Post hoc

```{r echo=FALSE}
adult_pairs_dominance <- pairs(emmeans(best_model_adult_face, ~ dominance | gender), adjust = "tukey")
summary(adult_pairs_dominance)
adult_pairs_gender <- pairs(emmeans(best_model_adult_face, ~ gender | dominance), adjust = "tukey")
summary(adult_pairs_gender)
```

### Plotting

```{r echo=FALSE}
cairo_pdf(
  filename            = "Figure3a.pdf",  # change as needed
  width               = 6,    # inches
  height              = 4,    # inches
  fallback_resolution = 600   # dpi for any bitmaps
)

ggplot(adult_face, aes(x=dominance, y=proportion_time, fill=gender)) +
  geom_boxplot() +
  stat_summary(fun=mean, geom="point", color="green", size=3, shape=18, position=position_dodge(width=0.75)) +
  ylim(0, 1) +
  labs(y = "Mean Proportion of Time", x = "Dominance", fill = "Gender") +
  scale_fill_discrete(labels = c("Female", "Male"))

dev.off()

```

### Conclusion

Two main effects (gender and dominance) and their interaction are significant. The preference for low dominance was only observed in female adults. The gender effect was only observed in high dominance faces.

## ROI

### Preprocess

```{r include=FALSE}
adult_ROI <- adult_df %>%
  select(sub, image_no, gender, Time_eye_h, Time_eye_l, Time_nose_h, Time_nose_l) %>%
  pivot_longer(
    cols = starts_with("Time"),  # Targeting all columns that start with "Time"
    values_to = "proportion_time",
    names_to = c("region", "dominance"),  # Splitting the column names into two new columns
    names_pattern = "^Time_(.*)_([hl])$"  # Regex to capture the region and dominance parts
  ) %>%
  mutate(
    dominance = case_when(
      dominance == "h" ~ "High",
      dominance == "l" ~ "Low"
    ),
    region = case_when(
      str_detect(region, "eye") ~ "Eyes",
      str_detect(region, "nose") ~ "Nose-Mouth"
    )
  )
```

### Model comparisons

```{r echo=FALSE}
best_model_adult_ROI <- compare_lmm_models(
  data = adult_ROI,
  dv = "proportion_time",
  fixed_effects = c("gender", "dominance", "region"),
  random_vars = c("dominance", "region"),
  group_var = "sub"
)

```

### The best model

```{r echo=FALSE}
summary(best_model_adult_ROI)
Anova(best_model_adult_ROI, type = 'III')
```

### Post hoc

```{r echo=FALSE}
adult_ROI_pairs_dominance <- pairs(emmeans(best_model_adult_ROI, ~ dominance | gender), adjust = "tukey")
summary(adult_ROI_pairs_dominance)
adult_ROI_pairs_gender <- pairs(emmeans(best_model_adult_ROI, ~ gender | dominance), adjust = "tukey")
summary(adult_ROI_pairs_gender)
```

### Plotting

```{r echo=FALSE}
cairo_pdf(
  filename            = "Figure3b.pdf",  # change as needed
  width               = 8,    # inches
  height              = 4,    # inches
  fallback_resolution = 600   # dpi for any bitmaps
)

ggplot(adult_ROI, aes(x=dominance, y=proportion_time, fill=gender)) +
  geom_boxplot() +
  facet_wrap(~ region) +
  stat_summary(fun=mean, geom="point", color="green", size=3, shape=18, position=position_dodge(width=0.75)) +
  ylim(0,1) +
  scale_fill_discrete(labels = c("Female", "Male")) +
  labs(y = "Mean Proportion of Time", x = "Dominance", fill="Gender") 

dev.off()
```

### Conclusion

The region effect is significant (eyes > nose-mouth) and it doesn't interact with other factors.

# Children

```{r include=FALSE}
# Read the CSV file, reading 'Age' as character temporarily
child_df <- read_csv('Children_data.csv', col_types = cols(
  Age = col_character()  # Specify Age to be read as character
))

# Check if 'age_group' column does not exist in the DataFrame
if (!"age_group" %in% colnames(child_df)) {

  child_df <- child_df %>%
    mutate(Age = as.numeric(gsub(",", ".", Age)),
           age_group = case_when(
             Age < 6 ~ "4-5y",
             Age >= 6 & Age < 7 ~ "6-7y",
             Age >= 7 ~ "7-9y"
             ))
  write_csv(child_df, 'Children_data.csv')
}

```


## Face

### Preprocess

```{r echo=FALSE}
child_face <- child_df %>%
  select(sub, image_no, gender, age_group, Time_face_h, Time_face_l) %>%
  pivot_longer(
    cols = c(Time_face_h, Time_face_l),
    names_to = "dominance", 
    values_to = "proportion_time"
  ) %>%
  mutate(dominance = case_when(
    dominance == "Time_face_h" ~ "High",
    dominance == "Time_face_l" ~ "Low"
  ))
```

### Model comparisons

```{r echo=FALSE}
best_model_child_face <- compare_lmm_models(
  data = child_face,
  dv = "proportion_time",
  fixed_effects = c("gender", "dominance", "age_group"),
  random_vars = c("dominance"),
  group_var = "sub"
)
```

### The best model

```{r echo=FALSE}
summary(best_model_child_face)
Anova(best_model_child_face, type='II')
```

### Pairwise
```{r}
children_pairs_age <- pairs(emmeans(best_model_child_face, ~ age_group, adjust = "tukey"))
summary(children_pairs_age)
```


### Plotting

```{r echo=FALSE}
cairo_pdf(
  filename            = "Figure4a.pdf",  # change as needed
  width               = 8,    # inches
  height              = 4,    # inches
  fallback_resolution = 600   # dpi for any bitmaps
)

ggplot(child_face, aes(x=age_group, y=proportion_time, fill=dominance)) +
  geom_boxplot() +
  facet_wrap(~gender, labeller = labeller(gender = c(M = "Male", F = "Female"))) +
  stat_summary(fun=mean, geom="point", color="green", size=3, shape=18, position=position_dodge(width=0.75)) +
  ylim(0, 1) +
  labs(y = "Mean Proportion of Time", x = "Age Group", fill = "Dominance")

dev.off()
```

### Conclusion

NO effect at all.

## ROI

### Preprocess

```{r include=FALSE}
child_ROI <- child_df %>%
  select(sub, image_no, gender, age_group, Time_eye_h, Time_eye_l, Time_nose_h, Time_nose_l) %>%
  pivot_longer(
    cols = starts_with("Time"),  # Targeting all columns that start with "Time"
    values_to = "proportion_time",
    names_to = c("region", "dominance"),  # Splitting the column names into two new columns
    names_pattern = "^Time_(.*)_([hl])$"  # Regex to capture the region and dominance parts
  ) %>%
  mutate(
    dominance = case_when(
      dominance == "h" ~ "High",
      dominance == "l" ~ "Low"
    ),
    region = case_when(
      str_detect(region, "eye") ~ "Eyes",
      str_detect(region, "nose") ~ "Nose-Mouth"
    )
  )
```

### Model Comparisons

```{r echo=FALSE}
best_model_child_ROI <- compare_lmm_models(
  data = child_ROI,
  dv = "proportion_time",
  fixed_effects = c("gender", "age_group", "dominance", "region"),
  random_vars = c("dominance", "region"),
  group_var = "sub"
)
```

### The best model

```{r echo=FALSE}
summary(best_model_child_ROI)
Anova(best_model_child_ROI, type = 'II')
```

### Pairwise
```{r}
children_ROI_pairs_age <- pairs(emmeans(best_model_child_ROI, ~ age_group, adjust = "tukey"))
summary(children_ROI_pairs_age)
```

### Plotting

```{r echo=FALSE}
cairo_pdf(
  filename            = "Figure4b.pdf",  # change as needed
  width               = 8,    # inches
  height              = 8,    # inches
  fallback_resolution = 600   # dpi for any bitmaps
)

ggplot(child_ROI, aes(x=age_group, y=proportion_time, fill=region)) +
  geom_boxplot() +
  facet_grid(gender~dominance, labeller = labeller(gender = c(M = "Male", F = "Female"))) +
  stat_summary(fun=mean, geom="point", color="green", size=3, shape=18, position=position_dodge(width=0.75)) +
  ylim(0, 1) +
  labs(y = "Mean Proportion of Time", x = "Age Group", fill = "Dominance")

dev.off()
```

### Conclusion

Still no dominance effect, but we found region effect (eyes > nose-mouth). We can argue that digit-tracking can capture certain effects but still we didn't find the dominance effect. We also find the age effect, which wasn't shown in the face analysis.
